Type theory in type theory using single substitutions

### 2023-12-27 main.tex
organise
stuff

@@

\author{Ambrus Kaposi}{Eötvös Loránd University, Budapest}{akaposi@inf.elte.hu}{https://orcid.org/0000-0001-9897-8936}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.

>>>>

\usepackage{agda}

@@

\author{Ambrus Kaposi}{Eötvös Loránd University, Budapest}{akaposi@inf.elte.hu}{https://orcid.org/0000-0001-9897-8936}
       {The author was supported by project no. TKP2021-NVA-29 which has been implemented with the support provided by the Ministry of Culture and Innovation of Hungary from the National Research, Development and Innovation Fund, financed under the TKP2021-NVA funding scheme.}
       %TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.
